qcircuit 2.5.3 Tutorial

### 2017-12-04 CO681-QuantumInformationProcessing/assignments/assignment_05.tex
finished a5

\begin{document}
\section{}
\subsection{a}
\paragraph{}
We have (leaving off normalization)
\begin{align*}
\ket{\phi^+} &= \ket{00} + \ket{11}\\
\ket{\phi^-} &= \ket{00} - \ket{11} \\
\ket{\psi^+} &= \ket{10} + \ket{01} \\
\ket{\psi^-} &= \ket{10} - \ket{01}
\end{align*}
So then
$$\ket{\phi^+}\bra{\phi^+} + \ket{\phi^-}\bra{\phi^-} + \ket{\psi^+}\bra{\psi^-} = \frac{1}{2}\begin{bmatrix}
2 & 0 & 0 &0 \\
0 & 1 & 1 & 0 \\
0 & 1 & 1 & 0 \\
0 &0 &0 &2
\end{bmatrix}$$
and 
$$\ket{\psi^-}\bra{\psi^-} =\frac{1}{2} \begin{bmatrix}
0 & 0 &0 & 0\\
0 & 1 & -1 & 0 \\
0 & -1 & 1 & 0 \\
0 &0 &0 &0
\end{bmatrix}$$
Hence our Werner state $\rho$ as a $4\times 4$ matrix is
$$\rho = \frac{1}{6}\begin{bmatrix}
2(1-p) & 0 & 0 &0 \\
0 & 1+2p & 1-4p & 0 \\
0 & 1-4p & 1+2p & 0 \\
0 & 0 & 0 & 2(1-p)
\end{bmatrix}$$
The partial transpose of $\rho$ is 
$$(I \otimes T)\rho = \frac{1}{6}\begin{bmatrix}
2(1-p) & 0 & 0 &1-4p \\
0 & 1+2p3 & 0 & 0 \\
0 & 0 & 1+2p & 0 \\
1-4p & 0 & 0 & 1-3p
\end{bmatrix}$$
\subsection{b}
The eigenvalues $(I \otimes T)\rho$ are $\frac{1+2p}{6}$, $0$, $0$, and $\frac{3-6p}{6} = \frac{1-2p}{2}$. The least of which is $\frac{1-2p}{2}$. From our slides we know that $\rho$ is separable if and only if $(I \otimes T)\rho$ is positive semidefinite. This happens if and only if $\frac{1-2p}{2} \geq 0$, that is when $p \leq 1/2$.

@@

@@

>>>>

\begin{document}
We have (leaving off normalization)
\ket{\phi^+} &= \ket{00} + \ket{11}\\
\ket{\phi^-} &= \ket{00} - \ket{11} \\
\ket{\psi^+} &= \ket{10} + \ket{01} \\
\ket{\psi^-} &= \ket{10} - \ket{01}
So then
$$\ket{\phi^+}\bra{\phi^+} + \ket{\phi^-}\bra{\phi^-} + \ket{\psi^+}\bra{\psi^-} = \frac{1}{2}\begin{bmatrix}
2 & 0 & 0 &0 \\
0 & 1 & 1 & 0 \\
0 & 1 & 1 & 0 \\
0 &0 &0 &2
\end{bmatrix}$$
and 
$$\ket{\psi^-}\bra{\psi^-} =\frac{1}{2} \begin{bmatrix}
0 & 0 &0 & 0\\
0 & 1 & -1 & 0 \\
0 & -1 & 1 & 0 \\
0 &0 &0 &0
\end{bmatrix}$$
Hence our Werner state $\rho$ as a $4\times 4$ matrix is
$$\rho = \frac{1}{6}\begin{bmatrix}
2(1-p) & 0 & 0 &0 \\
0 & 1+2p & 1-4p & 0 \\
0 & 1-4p & 1+2p & 0 \\
0 & 0 & 0 & 2(1-p)
\end{bmatrix}$$
The partial transpose of $\rho$ is 
$$(I \otimes T)\rho = \frac{1}{6}\begin{bmatrix}
2(1-p) & 0 & 0 &1-4p \\
0 & 1+2p3 & 0 & 0 \\
0 & 0 & 1+2p & 0 \\
1-4p & 0 & 0 & 1-3p
\end{bmatrix}$$
The eigenvalues $(I \otimes T)\rho$ are $\frac{1+2p}{6}$, $0$, $0$, and $\frac{3-6p}{6} = \frac{1-2p}{2}$. The least of which is $\frac{1-2p}{2}$. From our slides we know that $\rho$ is separable if and only if $(I \otimes T)\rho$ is positive semidefinite. This happens if and only if $\frac{1-2p}{2} \geq 0$, that is when $p \leq 1/2$.
\newpage

@@

\newpage

@@

We use throughout that $\ket{A}$ and $\ket{B}$ are orthogonal. We have that
$$-HU_0HU_f = (2\ket{\theta}\bra{\theta} - I_2)(2\ket{B}\bra{B} - I_2) = 4\ip{\theta}{B}\ket{\theta}\bra{B} - 2\ket{B}\bra{B} - 2\ket{\theta}\bra{\theta} + I_2.$$
Now we observe that
$\ip{\theta}{B} = \cos\theta$ and that
$$\ket{\theta}\bra{B} = \sin\theta\ket{A}\bra{B} + \cos\theta\ket{B}\bra{B}.$$
Further that
$$\ket{\theta}\bra{\theta} = \sin^2\theta\ket{A}\bra{A} + \sin\theta\cos\theta (\ket{A}\bra{B} + \ket{B}\bra{A}) + \cos^2\theta\ket{B}\bra{B}.$$
Then we see that
-HU_0HU_f &= 4\sin\theta\cos\theta\ket{A}\bra{B} + 4\cos^2\theta\ket{B}\bra{B} -2 \ket{B}\bra{B} \\
&-2\sin^2\theta\ket{A}\bra{A} -2\sin\theta\cos\theta(\ket{A}\bra{B} + \ket{B}\bra{A}) -2\cos^2\theta\ket{B}\bra{B} \\
&+ \ket{A}\bra{A} + \ket{B}\bra{B}\\
&= (1-2\sin^2\theta)\ket{A}\bra{A} +2\sin\theta\cos\theta\ket{A}\bra{B} - 2\sin\theta\cos\theta\ket{B}\bra{A} + (2\cos^2\theta-1)\ket{B}\bra{B}\\
&= \cos2\theta \ket{A}\bra{A} + \sin2\theta\ket{A}\bra{B} -\sin2\theta\ket{B}\bra{A} +\cos2\theta\ket{B}\bra{B}
as desired.
\newpage
First observe that
$$Tr(\rho) = \sum_j a_j Tr(E_j) = \frac{1}{d} \sum_j a_j$$
and then that
$$p(i) = Tr(\rho E_i) = ba_i + c \sum_{j\neq i} a_j = ba_i + c(dTr(\rho) - a_i) = ba_i + cd - ca_i.$$
Solving for $a_i$ we see that
$a_i = \frac{p(i) -cd}{b-c}.$
